
## Presidential elections


```{r}
examples=econIDV::Examples()
examples$election()
examples$election_env$attach()
```

### data preparation

```{r}
download_electionData()
# prepare choropleth map data
elections |>
  prepare_choroplethMapData() -> df_elections
df_elections |>
  prepare_fillColorByYears_data() -> df_elections_wider

# prepare datatable data
df_elections |>
  prepare_dataTableData() -> df_4dataTable_wide
```

### create sf 

```{r}
df_elections_wider |>
  as.data.frame() |> # to remove tibble class for row.names assignment
  create_sf() |>
  # 移除geometry空的資料, 否則ggplotly會有錯誤
  econIDV::remove_emptyGeometry() ->
  sf_elections_wider
```

<div class="alert alert-danger">
If `class(df_elections_wider)` has tibble class (i.e. tbl class), we won't be able to change row.names. Remove tibble class is necessary for the later sharedData creation.

If you are to use plotly to graph sf data, make sure there is no entry that has empty geometry.

</div>

### ggplot to plotly

```{r}
class(sf_elections_wider$y2012)
# is factor
```

```{r}
ggplot(data=sf_elections_wider)+theme_void() -> base
# as.is operator I(.) does not work as fill want, it would be come numeric unless as.character in advance.
list_gg=vector("list", 3)
base+
  geom_sf(
    aes(fill=I(as.character(y2012))),
    color="#828282", size=0.1) -> list_gg[[1]]
base+
  geom_sf(
    aes(fill=I(as.character(y2016))),
    color="#828282", size=0.1) -> list_gg[[2]]
base+
  geom_sf(
    aes(fill=I(as.character(y2020))),
    color="#828282", size=0.1) -> list_gg[[3]]

list_gg |> purrr::map(plotly::ggplotly) -> 
  list_ggplt
do.call(plotly::subplot, list_ggplt) -> plt0
# equivalent to `plotly::subplot(list_ggplt[[1]], list_ggplt[[2]], list_ggplt[[3]])`

plt0 |>
  plotly::layout(
    showlegend=F
  )
```

<div class="alert alert-info">
`I(.)` is an **as.is** operator, which prevent the function from changing its class. If there is no such change in the function, there is no effect from that. When using `I(.)` for fill aesthetics in ggplot or plotly, it will normally change the class to factor, then color according to factor attribute which is based on the type of the vector. When using `I(.)` with a character vector, the character values will be preserved for color interpretation. 
</div>


### direct plotly

```{r}
sf_elections_wider$y2012 
sf_elections_wider$y2012color = sf_elections_wider$y2012
levels(sf_elections_wider$y2012color) <- levels(df_elections$取色得票率區間)
sf_elections_wider$y2012color
```

```{r}
df_elections$取色得票率區間->
  df_elections$得票率區間
levels(df_elections$得票率區間) |>
  stringr::str_extract_all("[0-9]+") -> intervals
.x=1
purrr::map_chr(
  seq_along(intervals),
  ~{
    intervals[[.x]] |> 
    as.numeric() -> numberX
  paste0(min(numberX),"-",max(numberX),"%")
  }
) -> levelLabels
levels(sf_elections_wider$y2012color) <- levelLabels
sf_elections_wider$y2012color
sf_elections_wider$y2012
```

```{r}
plotly::plot_ly() |>
  plotly::add_sf(
    # name="2012",
    data=sf_elections_wider,
    split=~地區,
    color=~I(as.character(y2012)),
    alpha=1
  ) |>
  plotly::layout(
    colorway=
  )
```


```{r}
list_plt = vector("list", 3 )
plotly::plot_ly() |>
  plotly::add_sf(
    # name="2012",
    data=sf_elections_wider,
    split=~地區,
    color=~I(as.character(y2012)),
    alpha=1
  ) |>
  plotly::layout(
    xaxis=list(
      title=list(
        text="2012"
      )
    )
  )-> list_plt[[1]]
list_plt[[1]]
plotly::plot_ly() |>
  plotly::add_sf(
    data=sf_elections_wider,
    split=~地區,
    color=~I(as.character(y2016)),
    alpha=1
  ) |>
  plotly::layout(
    xaxis=list(
      title=list(
        text="2016"
      )
    )
  ) -> list_plt[[2]]
plotly::plot_ly() |>
  plotly::add_sf(
    data=sf_elections_wider,
    split=~地區,
    color=~I(as.character(y2020)),
    alpha=1
  ) |>
  plotly::layout(
    xaxis=list(
      title=list(
        text="2020"
      )
    )
  ) -> list_plt[[3]]

plotly::subplot(
  list_plt[[1]], list_plt[[2]], list_plt[[3]],
  titleX = T
) |> 
  plotly::style(
    line=list(
      width=0.2,
      color="#828282"
    )
  ) |> 
  plotly::layout(
    showlegend=F
  ) |>
  plotly::config(
    displayModeBar = FALSE
  )
```




### sharedData

row.names consistency
```{r}
# make row.names consistent across different to-be-shared data frames
row.names(df_4dataTable_wide) <- 
  df_4dataTable_wide$地區
row.names(sf_elections_wider) <-
  sf_elections_wider$地區

sharedData_elections_wider = crosstalk::SharedData$new(sf_elections_wider, group="election")
sharedData_dataTable = crosstalk::SharedData$new(df_4dataTable_wide, group="election")
```

```{r}
sharedData_elections_wider |> 
  directPlotlyPlot()  |>
  highlight(
    off="plotly_doubleclick"
  ) -> widgetPlolty
sharedData_dataTable |>
  DT::datatable(
    escape="地區" #不當HTML看待的欄位
    ) -> widgetDataTable

 crosstalk::bscols(
  widths=c(12, 12),
  widgetPlolty, widgetDataTable
) -> electionWidget
 
 electionWidget |> econIDV::showWidget()
```

```{r}
# undebug(subplot_titles)
tagList(
div(style="display:inline-block;width:650px;",
  subplot_titles(widget=widgetPlolty,
  titles=c("2012", "2016", "2020"))
  ),
div(style="display:inline-block;width:650px;",
  subplot_titles(widget=widgetPlolty,
  titles=c("2012", "2016", "2020"),
    leftpull=6))
) |> econIDV::showWidget()
```


```{r}
undebug(subplot_titles)
subplot_titles(
  widget=widgetPlolty,
  titles=c("2012", "2016", "2020"),
  leftpull=15, rightpull=8) |> 
  econIDV::showWidget()

```


```{r}
ui_container_labelsOnTop(widgetPlolty) |> econWeb::browseTag2()
```

```{r,echo=FALSE}
 
htmltools::save_html(electionWidget, "/Users/martinl/Github/econIDV/docs/election.html")
```
